### 2022-06-17 README.Rmd
v1.5.2 release check.
cv argument defaults to NULL.

## Overview
The R package **melt** provides a unified framework for data analysis with empirical likelihood methods. A collection of functions are available for basic regression analysis and hypothesis testing. Much of its functionality and syntax mimics the corresponding base R functions. The core computational routines are implemented with the 'Eigen' C++ library and 'RcppEigen' interface, with OpenMP for parallel computation. Additional functions are available for multiple testing for the analysis of experimental designs. Details of the testing procedures are given in [Kim et al. (2021)](https://arxiv.org/abs/2112.09206).

@@

# test of no treatment effect
lhs <- matrix(c(1, -1, 0, 0,
                0, 1, -1, 0,
                0, 0, 1, -1), byrow = TRUE, nrow = 3)
lht(fit3, lhs = lhs)

>>>>

## Overview
The R package **melt** provides a unified framework for data analysis with empirical likelihood methods. A collection of functions are available for regression analysis and hypothesis testing. Much of its functionality and syntax mimics the corresponding base R functions. The core computational routines are implemented with the 'Eigen' C++ library and 'RcppEigen' interface, with OpenMP for parallel computation. Additional functions are available for multiple testing for the analysis of experimental designs. Details of the testing procedures are given in [Kim et al. (2021)](https://arxiv.org/abs/2112.09206).

@@

# test of no treatment effect
lhs <- matrix(c(1, -1, 0, 0,
                0, 1, -1, 0,
                0, 0, 1, -1), byrow = TRUE, nrow = 3)
elt(fit3, lhs = lhs)
